\chapter{Introduction}

This document contains the result for the course \textit{High Performance Computing: Fluid Mechanics with Python} under Prof. Andreas Greiner at the University of Freiburg.
It consists of multiple experiments of fluid simulation in different settings.
The experiments include the \textit{Shear Wave Decay}, the \textit{Couette Flow}, the \textit{Poiseuile Flow} and the \textit{Sliding Lit}.
The \textit{Sliding Lit} differs from the other experiments, as it is parallelized because it takes very long to reach an equilibrium state.
\newline

The underlying concepts for the experiments are briefly described in \cref{ch:methods}.
If the reader wants to reproduce the experiments or extend the implementation, \cref{ch:implementation} helps to understand the code.
However, specific parameters for the experiments are listed next to the results.
\newline

All results are described in \cref{ch:results}, including plots of velocity-, density- or stream-fields of the simulated fluids.
A final evaluation of the results is located in \cref{ch:conclusion}.


\vspace{1cm}
\begin{tcolorbox}[colback=blue!20,%gray background
    colframe=black,% black frame colour
    width=\linewidth,% Use 5cm total width,
    arc=3mm, auto outer arc,
]
    \begin{centering}
        \textbf{Disclaimer: Usage of ChatGPT} \vspace{0.2cm} \\
        The text you are reading has undergone language enhancement by using ChatGPT, an AI-powered language model developed by OpenAI \cite{ChatGPT}.
        The primary purpose of this enhancement was to improve the text's clarity, readability, and grammar.
    \end{centering}
\end{tcolorbox}
